Operational constraints and closing civic space: International NGO restrictions and China’s Overseas NGO law

### 2023-12-07 manuscript/manuscript.qmd
Improve map fill and labeling

# Use aes(geometry) and stat = "sf_coordinates" to make geom_label_repel() work
# with geom_sf(): https://github.com/slowkow/ggrepel/issues/111#issuecomment-416853013
ggplot() +
  geom_sf(data = ongo_mapdata, aes(fill = ro_count), color = NA) +
  geom_sf(data = interior_borders, linewidth = 0.3, color = "white") +
  scale_fill_distiller(palette = "Reds", direction = 1, guide = "none", na.value = "gray80") +
  geom_label_repel(
    data = filter(ongo_mapdata, ro_count > 0),
    aes(label = ro_count, geometry = geometry),
    stat = "sf_coordinates", seed = 1234, label.size = 0.05, size = 3,
    color = "black", fill = scales::alpha("white", 0.7),
    segment.color = "black", segment.size = 0.25, min.segment.length = 0
  ) +
  coord_sf(crs = st_crs("EPSG:4480")) +  # China Geodetic Coordinate System 2000
  theme_void()
```

>>>>

ongo_mapdata <- ongo_mapdata |> 
  # Change provinces with 0 ONGOs to NA for plotting
  mutate(ro_count = ifelse(ro_count == 0, NA, ro_count)) |> 
  # Manually repel some provinces
  mutate(repel = case_when(
    province_en %in% c("Shanghai", "Tianjin") ~ "right",
    province_en == "Beijing" ~ "up",
    province_en == "Hebei" ~ "left",
    .default = "none"
  ))

# Use aes(geometry) and stat = "sf_coordinates" to make geom_label_repel() work
# with geom_sf(): https://github.com/slowkow/ggrepel/issues/111#issuecomment-416853013
ggplot() +
  geom_sf(data = filter(ongo_mapdata, !is_taiwan), aes(fill = sqrt(ro_count)), color = NA) +
  geom_sf(data = filter(ongo_mapdata, is_taiwan), fill = "gray70", color = NA) +
  geom_sf(data = interior_borders, linewidth = 0.3, color = "white") +
  scale_fill_distiller(palette = "Reds", direction = 1, guide = "none", na.value = "gray94") +
  geom_sf_label(
    data = filter(ongo_mapdata, ro_count > 0, repel == "none"),
    aes(label = ro_count),
    label.size = 0.05, size = 3, 
    color = "black", fill = scales::alpha("white", 0.8)
  ) +
  geom_label_repel(
    data = filter(ongo_mapdata, ro_count > 0, repel == "right"),
    aes(label = ro_count, geometry = geometry),
    stat = "sf_coordinates", seed = 1234, label.size = 0.05, size = 3,
    color = "black", fill = scales::alpha("white", 0.8),
    segment.color = "black", segment.size = 0.25, min.segment.length = 0,
    direction = "x", nudge_x = 1.5
  ) +
  geom_label_repel(
    data = filter(ongo_mapdata, ro_count > 0, repel == "left"),
    aes(label = ro_count, geometry = geometry),
    stat = "sf_coordinates", seed = 1234, label.size = 0.05, size = 3,
    color = "black", fill = scales::alpha("white", 0.8),
    segment.color = "black", segment.size = 0.25, min.segment.length = 0,
    direction = "x", nudge_x = -1.5
  ) +
  geom_label_repel(
    data = filter(ongo_mapdata, ro_count > 0, repel == "up"),
    aes(label = ro_count, geometry = geometry),
    stat = "sf_coordinates", seed = 1234, label.size = 0.05, size = 3,
    color = "black", fill = scales::alpha("white", 0.8),
    segment.color = "black", segment.size = 0.25, min.segment.length = 0,
    direction = "y", nudge_y = 1.5
  ) +
  coord_sf(crs = st_crs("EPSG:4480")) +  # China Geodetic Coordinate System 2000
  theme_void()
```
